\textit{Supporting information for}: How is experience transformed into memory?

### 2018-09-05 paper/supporting_information.tex
renamed supplemental materials supporting information
inputted andy's comments on main text

\title{\textit{Supplemental materials for}: How is experience transformed into memory?}
\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

The optimized model converged on 28 unique topics that were assigned non-zero weights over the course of the video.  We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.75\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 28 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}

@@

% Supplemental materials

>>>>

\title{\textit{Supporting information for}: How is experience transformed into memory?}
\author{Andrew C. Heusser, Paxton C. Fitzpatrick, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

The optimized model converged on 27 unique topics that were assigned non-zero weights over the course of the video.  We provide a list of the top ten highest-weighted words from each topic in Figure~\ref{fig:topics}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.75\textwidth]{figs/topic_words}
\caption{\small \textbf{Topics discovered in \textit{Sherlock}.} We applied a topic model to hand-annotated information about 1000 scenes spanning the 45 minute episode.  We identified 27 unique topics with non-zero weights (we used $K=100$ topics to fit the model).  Each topic comprises a distribution of weights over all words in the vocabulary.  For each topic, we show the words with the 10 largest weights, along with a suggested description of the topic.}
\label{fig:topics}
\end{figure}

@@

% Supporting information
